---
title: "Coordinate descent vs Proximal Operator"
author: "Fei Ding"
date: "2017年10月13日"
output: html_document
---


## Coordinate Descent vs Proximal Operator

This is the homework of the statistics computation

# The function of regularizing the data follows:
## The Function of Regularization
```{r Function of Regularization }

standvector = function(y){
  return(y-mean(y))
}

standmatrix = function(X){
  n=dim(X)[1]
  p=dim(X)[2]
  meanvec=c()
  squarevec=c()
  for(i in 1:p){
    X[,i]=X[,i]-mean(X[,i])
  }
  for(j in 1:p){
    squarevec=append(squarevec,sum(X[,j]*X[,j]))
  }
  for(k in 1:p){
    X[,k]=X[,k]/(sqrt(squarevec[k]/n))
  }
  return(X)
}

```

## The Parameters and the Generation of the Data

```{r}

n = 100
p = 500
sigma_noise = 0.5
beta = rep(0, p)
beta[1:6] = c(5,10,3,80,90,10)
X = matrix(rnorm(n*p,sd=10), nrow = n, ncol=p)
X_stand=standmatrix(X)
y = X_stand %*% beta + rnorm(n, sd = sigma_noise)
y_stand=standvector(y)
lambda = 0.2
maxinteration = 5000


```

## Using the Package-"dingfeicdpo" to Get the Beta

```{r}

library("dingfeicdpo")

betaHat1 = cdescent(y_stand, X_stand, lambda,maxinteration)
diff1 = unlist(betaHat1["cdescent_beta"]) - beta
L2Loss_cdescent = sqrt(sum(diff1^2))

#True Positive Rate
TP = sum(abs(beta)>0 & abs(unlist(betaHat1["cdescent_beta"]) )>0) / sum(abs(beta)>0)
# True Negative Rate
TN = sum(abs(beta)==0 & abs(unlist(betaHat1["cdescent_beta"]) )==0) / sum(abs(beta)==0)

# Compute Proximal Operator
betaHat2 = proxoperator(y_stand, X_stand, lambda,maxinteration)

diff2 = unlist(betaHat2["proxoperator_beta"]) - beta
L2Loss_proxoperator = sqrt(sum(diff2^2))

## Show the loss of the two methods
L2Loss_cdescent
L2Loss_proxoperator
```

## If you don't know the meaning of the function in the package,please try help("replaced by the name of the funciont")

##The Plot of the Comparation of Two Methods' Converagence Rate


```{r}
xlable = 1: maxinteration
plot(xlable,log10(unlist(betaHat1["cdescent_objectvalue"])),main="Coordinate Descent vs Proximal Operator",xlim=c(0,25),ylim=c(1.5,3.5),
     type="o",col=4, yaxs="i",xaxs="i",
     xlab="interations",ylab="objectvalue(log10 scale)",pch=20,cex = 0.7)


lines(xlable,log10(unlist(betaHat2["proxoperator_objectvalue"])),lwd=0.5,xlim=c(0,100),ylim=c(1.5,3.5),
    type="o",col=2, yaxs="i",xaxs="i",
     xlab="interations",ylab="objectvalue(log10 scale)",pch=20,cex = 0.7)

legend("topright", inset = 0.05,
       c("Coordinate Descent", "Proximal Operator"), lty = c(1, 1), pch = c(20, 20), col = c("blue",
                                                            "red"))

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
